---
title: 'Homework #1'
author: "Ximu Wang"
date: "2019/1/10"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question #1
#### Improt data.
```{r}
bf <- read.csv("BlackFriday.csv")
head(bf)
```

#### Observations and features.
```{r}
dim(bf)
```
So, there are 537577 observations and 12 features.

#### Nulls.
```{r}
is.null(bf)
```
This dataset has no null.
```{r}
length(bf[is.na(bf)])
```
So, this dataset has 540285 NAs.

#### Summary.
```{r}
summary(bf)
```

#### Summary of "Product_Category_1".
```{r}
summary(bf$Product_Category_1)
```

#### Datatype of "Age".
```{r}
typeof(bf$Age)
```

## Question #2
#### Convert the ‘Marital_Status’ column to a factor.
```{r}
bf$Marital_Status <- factor(bf$Marital_Status)
class(bf$Marital_Status)
```

## Question #3
#### Create a histogram of the ‘Purchase’ column using ggplot2.
```{r}
library(ggplot2)
ggplot(bf, aes(x=Purchase)) + geom_histogram(binwidth = 2)
```

## Question #4
#### Create a table to analyze the ‘City_Category’ column.
```{r}
city.table <- table(bf$City_Category)
city.table
```
## Question #5
#### Filter the dataset where Gender = M and Marital_Status = 1. How many observations are there?
```{r}
dim(bf[bf$Gender == "M",][bf[bf$Gender == "M",]$Marital_Status == 1,])[1]
```
So, there are 164537 observations.

#### Make a table of the age column. Which age group has the most observations?
```{r}
age.table <- table(bf$Age)
age.table[age.table == max(age.table)]
```
So, group "26-35" has the most observations.
